---
title: "Delgosha"
output: github_document
---
```{r include=FALSE}
knitr::opts_chunk$set( message=FALSE, warning=FALSE)
library(delgosha)
import_all_fonts()
```


<!-- badges: start -->

[![Lifecycle:
experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN
status](https://www.r-pkg.org/badges/version/instaloadeR)](https://CRAN.R-project.org/package=instaloadeR)
<!-- badges: end -->


Delgosha is an opinionated package which aims to provide a collection of ggplot2 themes for RTL languages (mostly Persian). 


## Installation

The package is not currently available on CRAN but you can install the package using the following line of code:

```{r eval=FALSE, include=TRUE}
remotes::install_github('mcnakhaee/delgosha')
```


## Usage

The package includes three types of functions:

- functions that start with `theme_` change the theme of the ggplot2 visualization. At the moment the following themes are included in the package: 

- functions that start with `import_` import necessary fonts for each theme included in the package.

- functions for palettes like many ggplot2 existing palettes start with `scale_`.


### Themes
The current list of themes include:

`theme_farsh_fa`

`theme_hamshahri`

`theme_hamshahri_modern`

`theme_digikala`

`theme_minimal_fa`

`theme_fa`

#### Examples

##### An example of farsh theme:

```{r fig.height=5, fig.width=7, message=FALSE, warning=FALSE,dpi=1000}
library(delgosha)
library(tidyverse)

spotify <- dadegan::spotify
spotify %>% 
  filter(artist_name %in% c('Alireza Eftekhari','Mohammadreza Shajarian','Alireza Ghorbani')) %>% 
  ggplot((aes(valence,popularity,color = artist_name_farsi))) +
  geom_point(alpha = 0.6,size = 3) +
  labs(x = 'شادی',
       y = 'محبوبیت',
       title = 'مقایسه ای بین محبوبیت و شادی آهنگ های سه خواننده محبوب سنتی',
       subtitle = '',
       caption =  'مصورسازی: محمد چناریان نخعی',
       color = '') +
  facet_wrap(~artist_name_farsi) +
  scale_color_farsh() +
theme_farsh_fa()
```


##### Hamshahri theme

Based on the main colors of Hamshahri news logo, I designed a theme for ggplot2. Note that this theme does not necessarily represent plots shown in Hamshahri (if such plots even exist!).

```{r fig.height=5, fig.width=7, message=FALSE, warning=FALSE, dpi=1000 }
factnameh <- dadegan::factnameh
tags_count <- factnameh %>%
  count(tags, sort = TRUE) %>%
  filter(!is.na(tags)) %>%
  slice(1:10) 


tags_count %>%
  ggplot(aes(fct_reorder(tags, n), n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = '',
    y = '',
    title = 'موضوعات با بیشترین تعداد درستی سنجی',
    subtitle = 'بیشترین برچسب هایی که در مقالات درستی سنجی وبسایت فکت نامه مورد استفاده قرار  گرفته اند.'
  ) +
  theme_hamshahri()
```

There is also modern version of Hamshari's theme which can be used by `theme_hamshahri_modern` function.

```{r fig.height=5, fig.width=7, message=FALSE, warning=FALSE, dpi=1000 }
tags_count %>%
  ggplot(aes(fct_reorder(tags, n), n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = '',
    y = '',
    title = 'موضوعات با بیشترین  تعداد  مقالات درستی سنجی شده',
    subtitle = 'بیشترین برچسب هایی که در مقالات درستی سنجی وبسایت فکت نامه مورد استفاده قرار  گرفته اند.',
    caption = 'منبع: وبسایت فکت نامه'
  ) +
  theme_hamshahri_modern()
```

#### Digikala theme

Based on the characteristics of plots used in their annual report I designed the following theme. Note that probably in the original Digikala's plots, the IranSans font is used which requires a proprietary license. So, I used the Yekan font in this theme.

```{r echo=TRUE, fig.height=5, fig.width=7, message=FALSE, warning=FALSE, dpi=1000}
tags_count %>%
  ggplot(aes(fct_reorder(tags, n), n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = '',
    y = '',
    title = 'موضوعات با بیشترین  تعداد  مقالات درستی سنجی شده',
    subtitle = 'بیشترین برچسب هایی که در مقالات درستی سنجی وبسایت فکت نامه مورد استفاده قرار  گرفته اند.',
    caption = 'منبع: وبسایت فکت نامه'
  ) +
  theme_digikala()
```


```{r echo=TRUE, dpi=1000}
library(Shafaf)
library(ggthemes)

research_studies %>% 
  count(`نام سازمان`, sort = TRUE) %>% 
  slice(1:10) %>% 
  ggplot(aes(x = `نام سازمان`, y = n ,fill = `نام سازمان` )) +
  geom_col(alpha = 0.5,show.legend = FALSE) +
  labs(title = 'سازمان های شهرداری با بیشترین تعداد پروژه تحقیقاتی',
       y = 'تعداد',
       caption = 'منبع: سایت شفاف شهرداری تهران') +
  scale_fill_tableau() +
  coord_flip()+
  theme_minimal_fa()
```

#### `theme_fa`

This theme can transform existing ggplot2 themes to a Persian theme.

```{r, fig.height=25,fig.width=25}
library(waffle)
colors <- c(
   'ahmadinejad' = '#F94144',
  'karrubi' = '#9c89b8',
  'mousavi' = '#43AA8B',
  'rezai' = '#577590',
  'voided_votes' = '#F3722C'
)

iran_election_2009 %>%
  ggplot(aes(fill = candidate, values = share_votes)) +
  geom_waffle(
    n_rows = 10,
    size = 2,
    make_proportional = TRUE,
    color = 'white',
    flip = TRUE
  ) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  scale_fill_manual(
    values = colors,
    labels = c('احمدی نژاد',
               'کروبی',
               'موسوی',
               'رضائی',
               'آرای باطله')
  ) +
  labs(title = 'سهم رای کاندیدهای ریاست جمهوری در انتخابات سال 88',
       fill = '') +
  facet_wrap(~ name_farsi) +
  theme_void() +
  theme_fa(
    strip_text_size = 25,
    plot_title_size = 35,
    plot_title_margin = 20
  ) +
  theme(
    plot.margin = margin(30, 30, 30, 30),
    legend.position = 'top',
    legend.text = element_text(size = 25, margin = margin(b = 10)),
    strip.text = element_text(margin = margin(t = 10, b = 10)),
    panel.spacing.x = unit(2, "lines"),
    panel.spacing.y = unit(2, "lines")
  )

  
```

#### Aljazeera theme

Based on Aljazeera's font.

```{r,   message=FALSE, warning=TRUE, dpi=1000}
library(quRan)
library(ggwordcloud)
library(tidytext)
quran_ar %>% 
  unnest_tokens(word,text) %>% 
  count(word,revelation_type,sort = TRUE) %>%
  slice(1:200) %>% 
  mutate(revelation_type = plyr::mapvalues(revelation_type,c('Medinan','Meccan'),c('مدني',
                                                                 'مكي'))) %>% 
  ggplot(aes(label = word,size = n,color = revelation_type)) +
  geom_text_wordcloud(family = 'Aljazeera') +
  scale_size_area(max_size = 15) +
  facet_wrap(~revelation_type) + 
  labs(title = 'سحابة كلمات في القرآن') + 
  theme_aljazeera()

```


### Fonts

Each theme uses a font which you might not have on your computer. If you don't have these fonts installed on your machine or loaded in your R session the plots will become ugly. So, first you need to install the fonts on your computer. you can run `import_{font_name}` functions to find where the fonts in the package are stored and install theme. After installing these fonts you can run `import_{font_name}` functions again to load the fonts into your R session.

For instance, you can load the vazir font used in farsh theme using the following function:

```{r eval=FALSE}
import_vazir()
```

Alternatively, you can import all fonts with the `import_all_fonts()` function.

### Issues and improvements

If you have found an issue you can send an email to mcnakhaee@gmail.com or you can open an issue in the package's github repository.


### License

This package is distributed under MIT License.



